Development of a 3D display

### 2016-05-18 paper.tex
Small fix
usage subsection, several small fixes

\usepackage{hyperref}

\usepackage[]{algorithm2e}

\usepackage{xspace}
\def \itwoc {I\textsuperscript{2}C\xspace}
\def \vdd {V\textsubscript{DD}}

@@

% In order to include images
\usepackage{graphicx}

@@

% To have text wrapped around images
\usepackage{wrapfig}

% Some parameters for wrapfig
\setlength{\intextsep}{0pt}%
\setlength{\columnsep}{15pt}%

% Same as regular math but with a bit of space before and after
\newenvironment{ownmath}
{\vspace{2mm}\hspace{15pt}\begin{math}}
{\end{math}\vspace{2mm}}

@@

% Introduction
% * after chapters to not number them
% TODO: don't show page numbers
\chapter*{Preface}

@@

First and foremost, I would like to express my gratitude to Mr. Patrick Spengler, my physics
teacher and the mentor of this thesis. Not only did he solve numerous malfunctions, but he also
is partly responsible for my interest in electronics and engineering.

@@

In the main loop of the program, this variable is continuously compared to \texttt{sinceMagnet}. If
sinceMagnet is bigger, the LEDs are refreshed by calling \texttt{sendData}. Within that function,
\texttt{nextPixelMicros} is incremented by \texttt{microsPerPixel}, causing the program to wait for
the display to turn another $\frac{1}{100}$ of a full circle. After that, it'll display the next
pixel.

@@

Initially, all my images were made completely by hand. I had to enter the individual bits into the
program that would result in the desired image. Obviously this was a time-consuming and error
prone task. In order to simplify the process of making an image, I wrote a python program that
would support me in doing so. All of the source code is available on \url{github.com/mbjd/_3DPOV}.

@@

The actual source code of the program outlined below is fully available on
\url{http://github.com/mbjd/\_3DPOV} in the folder \texttt{image\_creation}.

@@

\subsection{Ada colourditional functionality}

@@

>>>>

% A few useful definitions
\usepackage{xspace}
\def \itwoc {I\textsuperscript{2}C\xspace}
\def \vdd {V\textsubscript{DD}}

@@

% Needed to include images
\usepackage{graphicx}

@@

% To have text wrapped around figures
\usepackage{wrapfig}

% Some parameters for wrapfig
\setlength{\intextsep}{0pt}
\setlength{\columnsep}{15pt}

% Same as regular math but with a bit of space before and after, and indented a little
\newenvironment{ownmath}
{\vspace{2mm}\hspace{15pt}\begin{math}}
{\end{math}\vspace{2mm}}

\usepackage{listings} % For code snippets
% \usepackage{courier} % For monspaced code
\usepackage{inconsolata}
\lstset{basicstyle=\small\ttfamily,breaklines=true}
\usepackage[]{algorithm2e} % For pseudocode

@@

% * after chapters to not number them
\chapter*{Preface}

@@

First and foremost, I would like to express my gratitude to Mr. Patrick Spengler, my physics
teacher and the mentor of this project. Not only did he solve numerous malfunctions, but he also
is partly responsible for my interest in electronics and engineering.

@@

In the main loop of the program, this variable is continuously compared to \texttt{sinceMagnet}.
If \texttt{sinceMagnet} is bigger, the LEDs are refreshed by calling \texttt{sendData}. Within
that function, \texttt{nextPixelMicros} is incremented by \texttt{microsPerPixel}, causing the
program to wait for the display to turn another $\frac{1}{100}$ of a full circle. After that,
it'll display the next pixel.

@@

Initially, all my images were made completely by hand. I had to enter the individual bits into the
program that would result in the desired image. Obviously this was a time-consuming and error
prone task. In order to simplify the process of making an image, I wrote a python program that
would support me in doing so. All of the source code is available on
\texttt{github.com/mbjd/\_3DPOV} in the folder \texttt{image\_creation}.

@@

@@

\subsection{Additional functionality}

@@

\subsection{Usage}

This whole program is a python module, which is to say you can import it from any other python
program, including the interactive python shell.

\begin{lstlisting}
$ python
[...]
>>> from mkmodel import *
\end{lstlisting}
\vspace{-2mm}

After doing that, all of the functions defined in the program are available to play with. Using
the \texttt{newImage} function, an empty image can be generated. We then draw a line and a sphere
in the image:

\begin{lstlisting}
>>> img = newImage()
>>> drawLinePolar(img, (0, 7, 14), (30, 2, 14), green, 0.5)
>>> drawSpherePolar(img, (62, 4.5, 7), blue, 4.5)
\end{lstlisting}
\vspace{-2mm}

When the desired image is created, it can be saved as an Arduino program:

\begin{lstlisting}
>>> writeSketch(img, 'example')
\end{lstlisting}
\vspace{-2mm}

The complete program, ready to upload to the Teensy, is then saved in
\texttt{./example/example.ino}. Creating a directory for each program is necessary because the
Arduino IDE only opens them if they're located in a directory with the same name as the program.
